### 2014-05-29 ACL2014/system.tex
Vanilla LSH algorithm pseudo code

A family is generally interesting when  $P_1>P_2$. However, the difference between $P_1$ and $P_2$ can be very small. 
Given a family $H$ of hash functions with parameters ($R, cR, P_1,P_2$), 
\lsh algorithm is devised by amplifying the grap between the two probabilities $P_1$ and $P_2$. 
The pseudo code for vanilla \lsh is shown in Algorithm \ref{alg:vanilla-LSH}.

\mbox{Hadoop Vanilla \lsh} \\
\mbox{\small {\underline {MAP:}}} \\
  \FOR j:=1 \TO L \STEP 1 \\
	     $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$ \\

To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
Our framework has three main steps: 
i) Generate $256$ bit signature for each query.  
ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
Next, generate query pairs which fall in the same table.
iii) Compute cosine similarity between query points which fall in the same table and return the query pairs  
with similarity $\geq\tau$.

To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
Our framework has three main steps: 
i) Generate $256$ bit signature for each query.  
ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
Next, generate query pairs which fall in the same table.
iii) Compute cosine similarity between query points which fall in the same table and return the query pairs  
with similarity $\geq\tau$.

>>>>

A family is generally interesting when  $P_1>P_2$. However, the difference between $P_1$ and $P_2$ can be very small. 
Given a family $H$ of hash functions with parameters ($R, cR, P_1,P_2$), 
\lsh algorithm is devised by amplifying the grap between the two probabilities $P_1$ and $P_2$. 
The pseudo code written in distributed framework (Hadoop) for vanilla \lsh is shown below:

%in Algorithm \ref{alg:vanilla-LSH}.

{\bf MAP: Input: $N$ queries with their respective feature vectors} \\
\begin{itemize}
\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$, where $h_{1,j}(q),h_{2,j}(q),\dots,h_{k,j}(q)))$ are chosen at random from the \lsh family.
\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. All queries with similar $g_j$ functions ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
\end{itemize}

{\bf REDUCE: Input: Queries ($q=1,2,\dots,M$); $M$ is the number of test queries.} \\
\begin{itemize}
\item For each $j=1,2,\dots,L$
\begin{itemize}
\item Retrieve all the queries from the bucket with $g_j(q)$ function as the index of the bucket 
\item Compute cosine similarity between query q and all the retrieved queries. Return all the queries which have similarity affinity within a similarity threshold ($\tau$). 
\end{itemize}
\end{itemize}

%To solve the above problem, we propose a distributed Hadoop framework based on Locality Sensitive Hashing. 
%Our framework has three main steps: 
%i) Generate $256$ bit signature for each query.  
%ii) Use the $256$ bit signature for each query to generate $L$ tables for each table with $K$ bit signature. 
%Next, generate query pairs which fall in the same table.
%iii) Compute cosine similarity between query points which fall in the same table and return the query pairs  
%with similarity $\geq\tau$.
